\documentclass{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{array}

\begin{document}
\section*{\huge Mathematics Homework Sheet 7}
\begin{flushright}
   \textbf{Author: Abdullah Oguz Topcuoglu \& Yousef Farag}
\end{flushright}

\section*{Problem 1}

% TODO: first part not done

If \(b_n\) is convergent then
\[
   \liminf_{n \rightarrow \infty} b_n = \limsup_{n \rightarrow \infty} b_n = \lim_{n \rightarrow \infty} b_n
\]
From the first inequality we have
\[
   \limsup_{n \rightarrow \infty} (a_n + b_n) \leq \limsup_{n \rightarrow \infty} a_n + \lim_{n \rightarrow \infty} b_n
\]
And from the second inequality we have
\[
   \limsup_{n \rightarrow \infty} (a_n + b_n) \geq \limsup_{n \rightarrow \infty} a_n + \lim_{n \rightarrow \infty} b_n
\]
Combining these two inequalities we get
\[
   \limsup_{n \rightarrow \infty} (a_n + b_n) = \limsup_{n \rightarrow \infty} a_n + \lim_{n \rightarrow \infty} b_n
\]

\section*{Problem 3}
\(a_n\) is monotonically decreasing and \(\forall n \in N, a_n \geq 0\) and \(\lim_{n \rightarrow \infty} a_n = 0\). \\
We want to show that \(\sum_{n=1}^{\infty} (-1)^n a_n\) converges. \\
\[
   \sum_{n=1}^{\infty} (-1)^n a_n = - a_1 + a_2 - a_3 + a_4 - \ldots
\]
We can write this as
\[
   \sum_{n=1}^{\infty} (-1)^n a_n = - (a_1 - a_2) - (a_3 - a_4) - \ldots
\]
Since \(a_n\) is monotonically decreasing, we have
\[
   - (a_1 - a_2) - (a_3 - a_4) - \ldots \leq 0
\]
Because every paranthesis group is positive and they have minus sign before them so we are adding zero or negative terms. \\
Therefore, \(\sum_{n=1}^{\infty} (-1)^n a_n\) is bounded above by 0. \\
And we can also rewrite the sum as follows:
\[
   \sum_{n=1}^{\infty} (-1)^n a_n = -a_1 + (a_2 - a_3) + (a_4 - a_5) + \ldots
\]
Since \(a_n\) is monotonically decreasing, every paranthesis group is positive or zero. We are adding positive or zero elements to \(-a_1\)
which means the sum is greater or equal to \(-a_1\)
\[
   -a_1 \leq -a_1 + (a_2 - a_3) + (a_4 - a_5) + \ldots
\]
Therefore, \(\sum_{n=1}^{\infty} (-1)^n a_n\) is bounded below by \(-a_1\). \\
Let's take a look at odd and even indexed terms:
\[
   \sum_{n=1}^{\infty} (-1)^{2n} a_{2n} = a_2 + a_4 + a_6 + a_8 + \ldots \qquad (1)
\]
\[
   \sum_{n=1}^{\infty} (-1)^{2n+1} a_{2n+1} = -a_1 - a_3 - a_5 - a_7 + \ldots \qquad (2)
\]
Since \(a_n \geq 0\), (2) is monotonically decreasing and similarly (1) is monotonically increasing. \\
\\
\\
\[
   s_n = \sum_{k=1}^{n} (-1)^k a_k
\]
\[
   s_{2n} = \sum_{k=1}^{2n} (-1)^k a_k = (-a_1 + a_2) + (-a_3 + a_4) + \ldots
\]
\(s_{2n}\) is monotonically decreasing because every paranthesis group is negative or zero. So we are adding \(\leq 0\) elements each iteration
which means \(s_{2n} \geq s_{2(n+1)}\) \\
\\
\[
   s_{2n+1} = \sum_{k=1}^{2n+1} (-1)^k a_k = -a_1 + (a_2 - a_3) + (a_4 - a_5) + \ldots
\]
\(s_{2n+1}\) is monotonically increasing because every paranthesis group is positive or zero. So we are adding \(\geq 0\) elements each iteration
which means \(s_{2n+1} \leq s_{2(n+1)+1}\) \\
\\
And now it suffices to show that \(s_{2l-1} \leq s_{2l}, \forall l \in N\)
\begin{align*}
   s_{2l} &= \sum_{k=1}^{2l} (-1)^k a_k \\
   s_{2l - 1} &= \sum_{k=1}^{2l-1} (-1)^k a_k \\
   s_{2l} - s_{2l-1} &= \sum_{k=1}^{2l} (-1)^k a_k - \sum_{k=1}^{2l-1} (-1)^k a_k \\
   &= (-1)^{2l} a_{2l} + \sum_{k=1}^{2l-1} (-1)^k a_k - \sum_{k=1}^{2l-1} (-1)^k a_k \\
   &= (-1)^{2l} a_{2l} \\
   &= a_{2l} \\
   &\geq 0 \quad \text{because} \quad a_n \geq 0 \quad \forall n \in N
\end{align*}
Therefore, \(s_{2l-1} \leq s_{2l}, \forall l \in N\) \\
Therefore, \(\sum_{n=1}^{\infty} (-1)^n a_n\) converges. \\
I followed the hint in the homework sheet. \\

\end{document}